Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-09 02_Paper/paper.tex
ML methods

To study which implementation would be more suitable for industrial application, we compare Support Vector Machines (SVM), Multilinear Perceptrons as well as random forests on the task of quality prediction. All three will be introduced next.

>>>>

To study which implementation would be more suitable for industrial applications, we compare Multilinear Perceptrons (MLPs), Support Vector Machines (SVM), as well as random forests on the task of quality prediction. All three will be introduced next.
